MIRSVM: Multi-Instance Support Vector Machine with Bag Representatives

### 2017-09-22 ArticleRevision/article/article.tex
Added a missing comma

Instance-based methods under the SMI assumption attempt to identify desirable instance properties that make a bag positive. One traditional method is the Axis-Parallel Rectangle (APR) \citep{Dietterich1997}, which assigns a positive label to an instance if it belongs to an APR. The Diverse Density (DD){~\citep{Maron1998}} measure is maximized for instances that are near at least one instance in a positive bag and far from all instances in negative bags.~\citet{Auer2004} present a boosting approach that uses balls centered around positive bags, called Multi-Instance Optimal Ball (MIOptimalBall). A major challenge of these methods is that the distributions of positive and negative bags affect their performance~\citep{Chen2006,Chen2004}. Alternatively \citet{Fu2011} models the distribution of negative bags with Gaussian kernels, which can prove difficult when the quantity of data is limited.

>>>>

Instance-based methods under the SMI assumption attempt to identify desirable instance properties that make a bag positive. One traditional method is the Axis-Parallel Rectangle (APR) \citep{Dietterich1997}, which assigns a positive label to an instance if it belongs to an APR. The Diverse Density (DD){~\citep{Maron1998}} measure is maximized for instances that are near at least one instance in a positive bag and far from all instances in negative bags.~\citet{Auer2004} present a boosting approach that uses balls centered around positive bags, called Multi-Instance Optimal Ball (MIOptimalBall). A major challenge of these methods is that the distributions of positive and negative bags affect their performance~\citep{Chen2006,Chen2004}. Alternatively, \citet{Fu2011} models the distribution of negative bags with Gaussian kernels, which can prove difficult when the quantity of data is limited.
